---
title: "Thesis Schedule"
author: Jose P. Rizal
affiliation: University of the Philippines - Manila
format:
  pdf:
    number-sections: true
    colorlinks: true
---

# Research Timeline

```{r}
#| echo: false
#| output: false

options(scipen = 999)

# List of required packages
pkgs <- c(
  "dplyr",
  "kableExtra",
  "plan"
  )

# Install missing packages
missing_pkgs <- pkgs[!sapply(pkgs, requireNamespace, quietly = TRUE)]
if (length(missing_pkgs) > 0)
  install.packages(missing_pkgs)

# Load all packages
invisible(lapply(pkgs, library, character.only = TRUE))
```

```{r}
#| echo: false
#| warning: false

gt_object <- plan::read.gantt("../Gantt/workplan.csv") 

df_wp <- data.frame(
  task = gt_object@data$description,
  start_t = gt_object@data$start,
  end_t = gt_object@data$end,
  status = gt_object@data$done
)

colnames(df_wp) <- c("Task","Start Date", "End Date", "Status %")
```

The detailed tasks required to successfully complete this MS thesis are structured in @tbl-workplan, which delineates the tasks, start and end dates, and current completion status of each phase.

```{r}
#| label: tbl-workplan
#| tbl-cap: Workplan for MS Thesis
#| echo: false

kable(
  df_wp,
  format = "latex",
  longtable = TRUE,
  booktabs = TRUE,
  ) %>%
  row_spec(0, font_size = 10) %>%
  kable_styling(
    latex_options = c("repeat_header", "hold_position"),
    repeat_header_text = "\\textit{(Continued)}"
  )
  
```

# Gantt Chart

@fig-workplan presents a Gantt chart based on @tbl-workplan, effectively visualizing the project's operational timeline and task progress.

```{r, fig.width = 10, fig.height = 12}
#| label: fig-workplan
#| fig-cap: Timeline of activities for MS Thesis
#| echo: false
#| warning: false

p_work <- plot(
  gt_object,
  event.label='Thesis Defense',
  event.time='2026-10-05',
  col.event=c("blue"),
  col.done=c("lightblue"),
  col.notdone=c("beige"),
  main="MS Thesis Workplan"
)
legend(
  "topright",
  pch=22,
  pt.cex=2,
  cex=0.9,
  pt.bg=c("lightblue", "beige"),
  border="black",
  legend=c("Done", "Not Done"),
  bg="white",
  xpd=TRUE
)
```

